Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-22 paper/paper.tex
pass on 3.1

First, \tname{} analyzes the malicious traffic and extracts options
expressed in that traffic. Recall from
Section~\ref{sec:rules-and-packets} that rule options can be inferred
from packet contents. In this case, however, that information alone is
insufficient as the malicious traffic is characterized as a sequence
of 5K\Mar{really 5K?}\Mar{...and where did they come from?}
messages. \tname{} finds the following set of options at this stage by
analyzing the flow and contents of the messages:

@@

Finally, \tname{} ranks the inferred rules according to heuristics
learned from a database of existing rules. For example, one heuristic
function \tname{} uses for ranking leverages the amount of options a
rule of a given protocol typically has---the score of a rule on this
function is proportional to the popularity of the number of options it
declares. The list below shows the rule options for the top-5 rules
\tname{} produces for this attack.\Mar{algum problema em fazer isto?
  exemplos concretos ajudam muito!}

@@

\noindent
Note that, although options \CodeIn{dsize:0} and \CodeIn{itype:8} are
present in the set of inferred options, the others are not.  This
indicates, as expected, that the set of rule options is
overspecified. \tname{} produces the following five rules at the top
of the ranking after minimization and ranking.\Mar{eu ainda estou
  aguardando isto. A tabela 3 tambem nao indica o resultado!}

>>>>

First, \tname{} analyzes the malicious traffic and extracts options
expressed in that traffic. Recall from
Section~\ref{sec:rules-and-packets} that rule options can be inferred
from packet contents. In this case, however, that information alone is
insufficient as the malicious traffic is characterized as a sequence
of 5K\Mar{really 5K?}\Mar{...and where did they come from?} \Luc{Sim, floods podem ser compostos por milhares de pacotes, um dos datasets q encontrei possui mais de 500k pacotes de flood. Os datasets foram encontrados na internet.}
messages. \tname{} finds the following set of options at this stage by
analyzing the flow and contents of the messages:

@@

Finally, \tname{} ranks the inferred rules according to heuristics
learned from a database of existing rules. For example, one heuristic
function \tname{} uses for ranking leverages the amount of options a
rule of a given protocol typically has---the score of a rule on this
function is proportional to the popularity of the number of options it
declares. The list below shows the rule options for the top-5 rules
\tname{} produces for this attack.\Mar{algum problema em fazer isto?
  exemplos concretos ajudam muito!} \Luc{No caso desse ataque, a regra inicial possui apenas duas opcoes (sem contar o threshold). Entao existem apenas 3 combinacoes possiveis, dessas 3 apenas 2 sao capazes de isolar o ataque do trafego normal. Portanto, o top-2 eh:

  \CodeIn{...window:512; threshold: type both, track by\_dst, count 5000, seconds 3;...}

  \CodeIn{...flags: S; window:512; threshold: type both, track by\_dst, count 5000, seconds 3;...}
   }

@@

\noindent
Note that, although options \CodeIn{dsize:0} and \CodeIn{itype:8} are
present in the set of inferred options, the others are not.  This
indicates, as expected, that the set of rule options is
overspecified. \tname{} produces the following five rules at the top
of the ranking after minimization and ranking.\Mar{eu ainda estou
  aguardando isto. A tabela 3 tambem nao indica o resultado!}
  \Luc{Irei adicionar}
